Placeholder

### 2021-02-08 Paper_Histograms.Rmd
Filtered white and non-white participants from GLAD/EDGI, NBR and RAMP for ethnicity retro plot

ethnicity_levels <- c("White", "Asian or Asian British", "Black or Black British",
                      "Mixed or multiple ethnic origin", "Other")

GLAD.prepan %>% 
  ggplot(aes(x = Ethnicity_collapsed)) +
  geom_bar(fill = COPINGpalette6) +
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Ethnic distribution of the GLAD/EDGI prepan cohort",
       subtitle = paste("N =", dim(GLAD.prepan)[1]),
       x = "",
       y = "N participants") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2),
                   labels = ethnicity_levels)

@@

```{r GLAD/EDGI NBR and RAMP ethnicity}

dat.retro_ethnicity_plot <- dat.retro %>% 
  group_by(Sample_plot, Ethnicity_collapsed) %>% 
  summarise(n = n()) %>% 
  drop_na()

>>>>

GLAD.prepan_ethnicity_plot <- dat.retro %>% 
  mutate(Ethnicity_collapsed = 
           fct_recode(Ethnicity_collapsed,
             "White" = "European",
             "Asian or Asian British" = "Asian or Asian British",
             "Black or Black British" = "African or African British",
             "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
             "Other" = "Other"
           ))

GLAD.prepan_ethnicity_plot %>% 
  ggplot(aes(x = Ethnicity_collapsed)) +
  geom_bar(fill = COPINGpalette6) +
  theme_classic() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5)) +
  labs(title = "Ethnic distribution of the GLAD/EDGI prepan cohort",
       subtitle = paste("N =", dim(GLAD.prepan)[1]),
       x = "",
       y = "N participants") +
  scale_x_discrete(guide = guide_axis(n.dodge = 2))

@@

```{r Recode ethnicity levels and filter data}

dat.retro_ethnicity_plot <- dat.retro %>% 
  mutate(Ethnicity_collapsed = 
           fct_recode(Ethnicity_collapsed,
             "White" = "European",
             "Asian or Asian British" = "Asian or Asian British",
             "Black or Black British" = "African or African British",
             "Mixed or multiple ethnic origins" = "Mixed or multiple ethnic origins",
             "Other" = "Other"
           ))

#Filter White participants per sample

dat.retro_ethnicity_white <- dat.retro_ethnicity_plot %>% 
  group_by(Sample_plot, Ethnicity_collapsed) %>% 
  summarise(n = n()) %>% 
  drop_na() %>% 
  filter(Ethnicity_collapsed == "White")

#Filter non-white participants per study

dat.retro_ethnicity_non_white <- dat.retro_ethnicity_plot %>% 
  group_by(Sample_plot, Ethnicity_collapsed) %>% 
  summarise(n = n()) %>% 
  drop_na() %>% 
  filter(Ethnicity_collapsed != "White")

```{r Plot GLAD/EDGI NBR and RAMP ethnicity retro}
